Lobbying and Legislative Uncertainty

### 2016-05-09 presentation.tex
make adjustments to add simultaneous model to presentation

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
\author[Buzard and Saiegh \hspace{2.7in} \url{kbuzard@syr.edu}]{Kristy Buzard \inst{1} \and Sebastian Saiegh \inst{2}}
\institute{\inst{1} Syracuse University and The Wallis Institute \and \inst{2} UC San Diego}
\date{May 10, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\begin{frame}{Timeline}
\pause
\begin{enumerate}[<+->]
	\item {\bfseries Vote Buyer A}
		\begin{enumerate}[i.]
			%\pause
			\item Chooses bribes $\un{a} = \left(a_{-.5},a_0,a_{.5}\right)$
		\end{enumerate}
	%\pause
	\item \textbf{Vote Buyer B}
		\begin{enumerate}[i.]
			%\pause
			\item Observes $\un{a}$
			%\pause
			\item Chooses bribes $\un{b} = \left(b_{-.5},b_0,b_{.5}\right)$
		\end{enumerate}
	%\pause
	\item \textbf{Legislature}
	%\pause
		\begin{enumerate}[i.]
			\item All legislators observe $\un{a},\un{b}$
			\item Uncertainty about preferences realized: $\un{\ta} = \left(\ta_{-.5},\ta_0,\ta_{.5}\right)$
			\item Each legislator votes for her preferred policy 
		\end{enumerate}
\end{enumerate}
\end{frame}

@@

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\pause
\begin{itemize}[<+->]
	\item She gets to move first
	\item She wants $x$ to win instead of $s$
	\item Willingness-to-pay parameter $W_A$
\end{itemize}
\end{frame}

\section{Results}
\subsection{One Vote Buyer}
\begin{frame}{Two Non-Negative Bribes}

@@

\subsection{Two Vote Buyers}
\begin{frame}{Two Vote Buyers}
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{No Bribes}
  It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
\end{beamerboxesrounded}

@@

>>>>

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
\author[Buzard and Saiegh \hspace{3in} \url{kbuzard@syr.edu}]{Kristy Buzard\inst{1} \and Sebastian Saiegh\inst{2}}
\institute{\inst{1}Syracuse University and The Wallis Institute \and 
\inst{2}UC San Diego}
\date{May 10, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\begin{frame}{Timeline}
\pause
\begin{enumerate}[<+->]
	\item {\bfseries Vote Buyer A}
		\begin{enumerate}[i.]
			%\pause
			\item Chooses bribes $\un{a} = \left(a_{-.5},a_0,a_{.5}\right)$
		\end{enumerate}
	%\pause
	\item \textbf{Vote Buyer B}
		\begin{enumerate}[i.]
			%\pause
			\item Observes $\un{a}$ (in sequential model)
			%\pause
			\item Chooses bribes $\un{b} = \left(b_{-.5},b_0,b_{.5}\right)$
		\end{enumerate}
	%\pause
	\item \textbf{Legislature}
	%\pause
		\begin{enumerate}[i.]
			\item All legislators observe $\un{a},\un{b}$
			\item Uncertainty about preferences realized: $\un{\ta} = \left(\ta_{-.5},\ta_0,\ta_{.5}\right)$
			\item Each legislator votes for her preferred policy 
		\end{enumerate}
\end{enumerate}
\end{frame}

@@

\begin{frame}{Vote Buyer A}
\pause
Vote Buyer A is just like Vote Buyer B \textit{except}
\pause
\begin{itemize}[<+->]
	\item She gets to move first (in sequential model)
	\item She wants $x$ to win instead of $s$
	\item Willingness-to-pay parameter $W_A$
\end{itemize}
\end{frame}

\section{One Vote Buyer}
\subsection{}
\begin{frame}{Two Non-Negative Bribes}

@@

\section{Two Vote Buyers}
\subsection{Sequential Model}
\begin{frame}{Some Possibilities...}
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{No Bribes}
  It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
\end{beamerboxesrounded}

@@

\subsection{Simultaneous Model}
\begin{frame}{Some Possibilities...}
What I know...
\begin{itemize}
	\item FOCs look the same as for one vote buyer, e.g.
		\begin{equation*}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
		\end{equation*}
			\begin{itemize}
				\item Two roots, only larger one satisfies SOC
			\end{itemize}
\end{itemize}
